### 2025-01-17 manuscript.tex
LOB data collection methods explained.

\section{The data}
The Trader Workstation (TWS) is an online platform created by Interactive Brokers (IBKR) that traders and investors use to trade stocks, bonds, futures, and more across over 150 markets worldwide via its graphical user interface. \cite{TW} TWS also offers a non-graphical API designed for fast-paced, data-sensitive, and complex programmatic trading. This API can handle thousands of market data streams simultaneously while allowing users to execute trades. \cite{IBKRAPI}.\\ 
Using this API, various types of data can be collected, including Top Market Data (Level 1) and Market Depth data (Level 2). Level 1 data includes the best bid and ask prices, along with the number of shares that traders are trying to buy or sell. It essentially represents the top of the limit order book for both sides. \cite{IL1} Level 2 data expands the information provided by Level 1 by adding the market depth, typically showing about 5-10 additional price levels. This type of data includes not only the best bid and ask prices but also some of the subsequent lines in the limit order book. \cite{IL2}\\
HOW LIMIT ORDER BOOKS ARE LOADED\\
EXPLAIN THE STRUCTURE AND MEANING OF OUR DATA\\
PIC OF DATA?\\

>>>>

\section{The data}
The Trader Workstation (TWS) is an online platform created by Interactive Brokers (IBKR) that traders and investors use to trade stocks, bonds, futures, and more across over 150 markets worldwide via its graphical user interface. \cite{TW} TWS also offers a non-graphical API designed for fast-paced, data-sensitive, and complex programmatic trading. This API can handle thousands of market data streams simultaneously while allowing users to execute trades. \cite{IBKRAPI}.\\ 
Using this API, various types of data can be collected, including "Top Market Data" (Level 1) and "Market Depth" data (Level 2). Level 1 data includes the best bid and ask prices, along with the number of shares that traders are trying to buy or sell. It essentially represents the top of the limit order book for both sides. \cite{IL1} Level 2 data expands the information provided by Level 1 by adding the market depth, typically showing about 5-10 additional price levels. This type of data includes not only the best bid and ask prices but also some of the subsequent lines in the limit order book. \cite{IL2}\\
!!!!!!!!!!!!REFACTOR THIS PARAGRAPH!!!!!!!!!!:Generally, there are two common methods for collecting order book data: the user can either request full snapshots of the limit order book (LOB) or receive updates through streams of messages. The latter offers a more optimized approach, as repeatedly requesting full snapshots in a liquid market would impose a high computational load due to the large number of changes occurring every second. To mitigate this, snapshots are returned at discrete time intervals. However, the downside is that between snapshots, it is impossible to track the changes, significantly reducing the available information. \cite{TLOB} A subset of the IBKR API, known as the TWS API, allows the collection of market depth data from the LOB as streams of messages, with each message including the order's ID, date, type, price, and size. \cite{TWS_API_MD}\\
EXPLAIN THE STRUCTURE AND MEANING OF OUR DATA\\
PIC OF DATA?\\
